Article title

### 2017-06-27 paper-webserver.tex
CHANGE: citation

Subtyping and other analyses software often require command-line or programming experience. To make such \textit{in-silico} techniques user-friendly for front-line clinicians and laboratories, a variety of web services have been developed in Denmark \cite{joensen2014real}, Canada \cite{whiteside2016superphy}, and in collaborations \cite{hasman2015detection}. While useful, argubly \cite{fricke2014bacterial}, the lack of bioinformatic standards and common infrastructure technologies have made it difficult to fully leverage the big-data results from WGS.

>>>>

Subtyping and other analyses software often require command-line or programming experience. To make such \textit{in-silico} techniques user-friendly for front-line clinicians and laboratories, a variety of web services have been developed in Denmark \cite{joensen2014real}, Taiwan \cite{liu2016construction}, and in collaborations \cite{hasman2015detection}. While useful, argubly \cite{fricke2014bacterial}, the lack of bioinformatic standards and common infrastructure technologies have made it difficult to fully leverage the big-data results from WGS.
